Example Paper\thanks{\acknlowledgements}

### 2024-01-19 latex-article/article.tex
Add biblatex option
Fix enumerate subitem and subsubitem color

\documentclass[12pt]{article}
\usepackage{paper}
\usepackage{math}

\title{Example Paper\thanks{\acknlowledgements}}
\author{
  Author One\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} 
  \ and 
  Author Two\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
}
\date{\textsc{\today}}
\def\acknlowledgements{%
  Acknlowedgements
}

@@

Hi and welcome to my default paper template. I tried to make the theme minimal and beautiful while able to do all the things that I want it to do. These include making it easy to make figures/tables with notes; have powerful math commands; have nice readable typography; make co-authoring in a document easy; have a nice looking bibliography; and make appendices easy.\kyle{I'm including this comment for coauthors. If I switch above to \texttt{togglefalse}, this will dissapear.}  I'll show off these things, but make sure to check the source code alongside to see how simple it is to typset with this.

@@

% ------------------------------------------------------------------------------
\newpage
\bibliography{references.bib}
% ------------------------------------------------------------------------------

>>>>

\documentclass[12pt]{article}
\usepackage{paper}
\usepackage{math}
\addbibresource{references.bib}

\title{Example Paper\thanks{\acknlowledgements}}
\author{
  Author One%
  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} 
  \ and 
  Author Two%
  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
}
\date{\textsc{\today}}
\def\acknlowledgements{%
  Acknlowedgements
}

@@

Hi and welcome to my default paper template. I tried to make the theme minimal and beautiful while able to do all the things that I want it to do. These include making it easy to make figures/tables with notes; have powerful math commands; have nice readable typography; make co-authoring in a document easy; have a nice looking bibliography; and make appendices easy. \kyle{I'm including this comment for coauthors. If I switch above to \texttt{togglefalse}, this will dissapear.} I'll show off these things, but make sure to check the source code alongside to see how simple it is to typset with this.

@@

% ------------------------------------------------------------------------------
\newpage
% \bibliography{references.bib}
\printbibliography
% ------------------------------------------------------------------------------
